Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-17 ms.tex
fixed stag radius

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
% \usepackage{natbib}

@@

Here we summarize analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.  Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter (eq.~[\ref{eq:dsdt}])
\begin{eqnarray}
v_{\rm w} = v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2} 
 \approx v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right)^{1/2},
\end{eqnarray}
where the parameter $\vwO = 500 v_{500}$ km s$^{-1}$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).

@@

Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs})
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
\times 10^6\ \, v_{500}^2 \,\,{\rm K} 
\label{eq:Tanalytic}
\end{align}
%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs})
\begin{align}
  \frac{\rs}{\rsoi}=\frac{\sigma^{2}}{2 v_{w,0}^{2} n}\left[
   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right],
 \label{eq:stag_analytic}
\end{align}
in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the
density profile at $r = r_{\rm s}$, and A and B are constants that depend on the Nuker
parameter $\Gamma$ and the adiabatic index of the gas.

If the SMBH dominates the gravitational potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg \sigma$) then equation (\ref{eq:stag_analytic}) simplifies greatly
\begin{align}
  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2} \approx 6
 \, \pc \,\, \Mbheight v_{500}^{-2},
  \label{eq:stag_simple}
\end{align}
where the numerical estimate assumes $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).  In the opposite limit when the wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.

@@

The SMBH accretion rate is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where we have made use of equation (\ref{eq:stag_simple}), i.e. assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
    2.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}

@@

>>>>

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

Here we summarize analytic estimates of physical quantities, such as the stagnation radius $\rs$ and the mass accretion rate, the detailed derivation of which are given in Appendix \ref{app:rs}.  Our results are expressed in terms of the SMBH mass $M_{\bullet} = 10^{8}M_{\bullet,8}M_{\odot}$ and the wind heating parameter (eq.~[\ref{eq:dsdt}])
\begin{eqnarray}
v_{\rm w} &=& v_{\rm w,0}\left(1+\frac{\sigma^{2}}{v_{\rm w,0}^{2}}\right)^{1/2}  \nonumber \\
 &\approx& v_{\rm w,0}\left(1+0.14 \Mbheight^{0.43}\left[\frac{v_{w,0}}{500\,\rm km\,s^{-1}}\right]^{-1}\right)^{1/2},
\end{eqnarray}
where we remind that the parameter $\vwO$ accounts for wind heating beyond the baseline level produced by the winds of old stars, and the final equality makes use of $M_{\bullet}-\sigma$ (eq.~[\ref{eq:Msigma}]).

@@

Continuity of the entropy derivative at the stagnation radius demands that the temperature at the stagnation radius is given by (Appendix \ref{app:rs}, eq.~[\ref{eq:first_law}])
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
\times 10^6\ \, v_{500}^2 \,\,{\rm K} 
\label{eq:Tanalytic}
\end{align}

Hydrostatic equilibrium can be used to determine the location of the stagnation radius where $v = 0$ (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
\rs=\frac{G \Mbh}{n \vw(\rs)^2}\left(\frac{9-\Gamma}{2} \frac{\Mstar(\rs)}{\Mbh} +\frac{7}{2}\right),
\label{eq:stag_analytic})
\end{align}
in terms of the radius of the sphere of influence (eq.~[\ref{eq:rsoi}]), where $n$ is the power-law slope of the density profile at $r = r_{\rm s}$.

If the SMBH dominates the gravitational potential at the stagnation radius ($M_{\bullet} \gg M_{\star}$; $v_{w,0} \gg \sigma$) then equation (\ref{eq:stag_analytic}) simplifies greatly
\begin{align}
  &\rs=\frac{7}{2}\frac{G \Mbh}{n v_{\rm w}^{2}} \approx 6
 \, \pc \,\, \Mbheight v_{500}^{-2},
  \label{eq:stag_simple}
\end{align}
where the numerical estimate assumes $n = 1$.  This expression is similar to that obtained by \citet{Volonteri+11} on heuristic grounds (their equation~[6]).  In the opposite limit when the wind heating is weaker ($v_{\rm w,0} \ll \sigma$), the stagnation radius moves to very large radii or may not exist at all.

@@

The SMBH accretion rate is given by the integrated mass loss rate interior to the stagnation radius (eq.~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where we have made use of equation (\ref{eq:stag_simple}), i.e. assuming that $v_{w,0} \gg \sigma$.  The resulting Eddington ratio $\eddr$ is given by 
\begin{eqnarray}
\frac{\dot{M}}{\dot{M}_{\rm edd}} &\approx&
  \begin{cases}
    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
    2.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}
To reproduce the estimated values $\sim 10^{-XX}$ in low luminosity AGN, we thus require $v_{w,0} \sim $.  {\bf BDM: put some realistic numbers, e.g. from Ho 2009 or better references}

@@

\begin{deluxetable}{lccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Results
\label{tab:surveys}}
\tablehead {
\colhead{Name}           &
\colhead{Ang.~Res.}  &
\colhead{$\nu$}          &
\colhead{F$_{\rm lim}^{(a)}$}               & 
\colhead{Area}          &
\colhead{$\Delta T$$^{(c)}$}            &
%\colhead{$T$$^{(d)}$}        &
\colhead{N$_{\rm obs}$$^{(e)}$}        &
\colhead{ref.}           
}
\startdata
\colhead{}           &
\colhead{(arcsec)}  &
\colhead{(GHz)}          &
\colhead{(mJy)}               & 
\colhead{(deg$^{2}$)}          &
\colhead{(d)}            &
%\colhead{(yr)}      &       
\colhead{}      \\
\hline
LOFAR & 80 & 0.15 & 11 & 1500 & 30 & 36 & 1\\
LOFAR-Expanded  & - & - & 1.1 & $10^{4}$  & 30  & 36 & -\\
VAST-Wide  & 10 & 1.3 & 0.5 & 10$^{4}$ & 1   & 1096 & 2\\
VAST-Deep & - & - & 0.05 & -  & 365  & 4 & - \\
VAST-Deep Single Field & - & - & - & -  & 1  & 365 & - \\
VLASS-Wide  & 2 & 3 & 0.1 & $10^{4}$ & 365  & 4 & - \\
VLASS-Deep  & 0.6 & - & 0.003 & 10  & 365  & 4 & - \\
%VLASS-Deep-Short  & - & - & 0.01 & 40  & 10  & 10 & - \\
%CMB50cm  & 840 & 150 & 3.2 & 10$^{4}$  & 1  & 1096 & - \\
%CMB2m  & - & - & 1.0 & -  & -  & - & - \\
CMB-fast  & 840 & 150 & 1.0 & 10$^{4}$  & 1  & 1096 & - \\
CMB-deep  & - & - & 0.1 & -  & 100  & 11 & - \\
\enddata
\tablecomments{Put Results Here}
\end{deluxetable}
